---
title: "Preliminary Regression"
output: 
  html_notebook: 
    code_folding: hide
    theme: journal
    toc: yes
---
# Variable Description
```{r}
col_labs <- c("Registr Length", "Price Update", "Initial Return", "Insider Sale", "CAR (Publish)","Volat (half1)", "Volat (half2)", "AbnRet (half1)", "AbnRet (half2)")
varnames <- data.frame(Variable = col_labs)
varnames$Descrition <- c("Log(Registration Period, days)", "Price Update, %", "Initial Return", "Dummy if there were insider sales at the end of lockup", "CAR during 5 days after letter publication","Stocks volatility in the first half of the first year", "Stocks volatility in the second half of the first year", "Abnornal stock returns (vs Size&BM) in the first half of the first year", "Abnornal stock returns (vs Size&BM) in the second half of the first year")
print(varnames)
```

# TABLE 1. OLS Regressions of the Full Sample
Our OLS results are the same as in the previous version of the paper.

More SEC Comment letters is associated with:

1. Longer Resitration Period
2. Lower Price Update
3. Higher Chances of Insider Sales at the end of the Lock Up 
4. Higher Volatility (during the year, first halfyear, second halfyear)

And there are no relation with:

* All types of returns: Initial returns, returns around letter disclosure, abnormal returns

**ALL results here are very robust to subsampling, controls etc.**
```{r, include=FALSE}
require(data.table)
require(lubridate)
require(psych)
require(data.table)
ipo <- data.table(read.csv("/Users/orhahog/Dropbox/Projects/SEC Letter Project/Data After Review/ipo_20170620.csv"))
wina <- 0.001
lwin <- function(x, a = wina) return(winsor(log(1+x),a))
w <- function(x, a = wina) return(winsor(x,a))

### censor sample here
ipo1 <- ipo[ymd(Filing_date) > ymd("20050512")  & ymd(Issue_date) < ymd("20161231")] 
ipo1[, `:=` (author_count = .N), by = letter_author]
#ipo1 <- ipo1[author_count >= 5]

ipo1[, `:=` (log_sale = lwin(sale), n_segments = w(n_segments), age = lwin(Year - founding_year), UW_rank = w(UW_rank), price_update = w(price_update), F_score = w(F_score),law_rank = w(Law.firm.5years),
             log_S1_words = lwin(S1_words), S1_un = w(S1_uncertanty), log_words = lwin(Upload1_words), log_n_letters = lwin(n_letters), log_n_letters_after = lwin(n_letters_after_price),
             registration_length = w(registration_length), log_registration_length = lwin(registration_length), ret_publish = w(ret_publish), vol_half1 = w(vol_half1), vol_half2 = w(vol_half2))]

end_OLS <- " ~  log_sale + n_segments + age +  UW_rank + law_rank + VC + JOBS + log_S1_words + 
S1_un + log_n_letters|FF_48 + Year + AD_Office|0|FF_48"
dep_vars <- c("log_registration_length","price_update", "IR", "insider_sales", "ret_publish", "vol_half1","vol_half2", "ret_abn_175", "I(ret_abn_365 - ret_abn_175)")
#col_labs <- c("Registr Length", "Price Update", "Initial Return", "Insider Sale", "CAR (Publish)","Volat (half1)", "Volat (half2)", "AbnRet (half1)", "AbnRet (half2)")
var_labs <- c("# Letters, log", "Sales", "# Segments", "Age", "UW Rank", "Law Rank", "VC Dummy",
               "JOBS Act", "S1 Length", "S1 Uncertanty")
fe_lines <- list(c("Year FE", rep("YES",length(col_labs))), c("Ind (FF-48) FE", rep("YES",length(col_labs))), c("SEC Office FE", rep("YES",length(col_labs))))
require(lfe)
require(stargazer)
my_felm <- function(x) felm(as.formula(unlist(x)), data = ipo1)
line <- lapply(dep_vars, function(x) return(paste0(x, end_OLS)))
model <- lapply(line, my_felm)
````

```{r results='asis'}
table1 <- stargazer(model, type = "html",  omit.stat = c("ser", "f"), covariate.labels =  var_labs,
                    column.labels = col_labs, dep.var.labels.include = F, title = "Table 1. OLS Results", add.lines = fe_lines, order = c(10, 1:9))
```




```{r, include=FALSE}
end_2SLS <- " ~  log_sale + n_segments + age +  UW_rank + law_rank + VC + JOBS + 
log_S1_words + S1_un |FF_48 + Year + AD_Office|(log_n_letters  ~ letter_author)|FF_48"
line2 <- lapply(dep_vars, function(x) return(paste0(x, end_2SLS)))
model2 <- lapply(line2, my_felm)
```

# TABLE 2. 2SLS Regressions of the Full Sample
Letter-writer fixed effects are used as instrumental variables for the number of SEC Comment letters.

In the causal effect specification there are two very strong results. One additional "random" letters 
would cause **longer** registration, but would results at **higher** returns around the letter disclosure. (strong results)

And there are two results which come and go in some specifications. One additional "random" letter would cause
**lower** initial returns and **higher** volatility in the second half of the first year. (weak results, change with specification)
```{r results='asis'}
table2 <- stargazer(model2, type = "html",  omit.stat = c("ser", "f"), covariate.labels =  var_labs,
                    column.labels = col_labs, dep.var.labels.include = F, title = "Table 2. 2SLS Results", add.lines = fe_lines, order = c(10, 1:9))

```

# TABLE 3. OLS Regressions of the Subsample with Returns on the Letter Disclosure Dates Above Median.

Because results on the disclosure date seems to be interesting I run the same test for IPOs with the cummulative abnormal returns after the letter disclosure are above the median value. In these table I have half of IPOs with relativelly "good" SEC letters.

**OLS resutls in this subsample are the same as in the full sample**
```{r results='asis'}
ipo2 <- ipo1[ ret_publish >= median(ret_publish)]
my_felm <- function(x) felm(as.formula(unlist(x)), data = ipo2)
line3 <- lapply(dep_vars, function(x) return(paste0(x, end_OLS)))
model3 <- lapply(line3, my_felm)

table3 <- stargazer(model3, type = "html",  omit.stat = c("ser", "f"), covariate.labels =  var_labs,
                    column.labels = col_labs, dep.var.labels.include = F, title = "Table 3. OLS Results (High Disclosure Returns)", add.lines = fe_lines, order = c(10, 1:9))
```

```{r, include=FALSE}
ipo2 <- ipo1[ ret_publish >= median(ret_publish)]
my_felm <- function(x) felm(as.formula(unlist(x)), data = ipo2)
line4 <- lapply(dep_vars, function(x) return(paste0(x, end_2SLS)))
model4 <- lapply(line4, my_felm)
```

# TABLE 4. 2SLS Regressions of the Subsample with Returns on the Letter Disclosure Dates Above Median.

Here similar to the previous table I restrict the sample to companies that had CAR during five days
from the disclosure of first letter above the median. Therefore this subsample inlcudes IPOs with relativelly 
"good" letters. 
Unlike previous table number of letters is instrumented with the letter-writer fixed effects.

When one additional "good" letter is sent randomly:

1. Registration is longer (like in OLS)
2. Price Update is lower (like in OLS)
3. Lower initial returns (!!! not like in OLS)
4. Higher volatility and initial returns in the second half of the year (!!! not like in OLS)
```{r results='asis'}
table4 <- stargazer(model4, type = "html",  omit.stat = c("ser", "f"), covariate.labels =  var_labs,
                    column.labels = col_labs, dep.var.labels.include = F, title = "Table 4. 2SLS Results (High Disclosure Returns)", add.lines = fe_lines, order = c(10, 1:9))
```